% @Author: Jacem Chaieb
% @Date:   2015-07-26 13:42:06
% @Last Modified by:   Jacem Chaieb
% @Last Modified time: 2016-04-12 15:43:36
\chapter*{Dedication}

\thispagestyle{empty}
%
%For all they have endured satisfying all my needs and wishes
\begin{center}
  I would like to dedicate this modest work, the fruit of my efforts and my success: ~\\
  
\vspace{2\baselineskip}


  \textbf{To my very dear father}, as a token of my affection and my
gratitude for all the sacrifices made for my education ~\\
  and to whom I owe my success. ~\\
  \vspace{2\baselineskip}

  \textbf{To my very dear mother}, who has never ceased to surround me with her ~\\
  affection, support, and love. ~\\
    \vspace{2\baselineskip}

  \textbf{To my dear sister}, who has always
surrounded by her support and affection, thank you for always being there for me, ~\\
  to help me get through the tough times. ~\\
      \vspace{2\baselineskip}

  \textbf{To my best friends}, who have proven that it is love that
weave family ties and not blood, for the memories we have shared, ~\\
   to whom I wish good luck and success. ~\\
         \vspace{2\baselineskip}

To all my family and all those I love, ~\\
  
\end{center}
%
\nopagebreak{%
  % And maybe a quote here
  \raggedright\hspace{5.75cm} To all of you,~\\
  \raggedright\hspace{7.75cm} I dedicate this work\@.~\\~\\~\\
  %
  \raggedleft\normalfont\large\itshape{} \reportAuthor\par%
}
%
%
%
%
%
%
\chapter*{Thanks}
\thispagestyle{empty}
%
\begin{center}
At the end of this work, I would first like to thank ~\\

\textbf{GOD}, for empowering me to be who I am today, ~\\

\textbf{(Al-hamdullah)}. ~\\
         \vspace{2\baselineskip}

Then, I would like to express my sincere thanks to
all the people who have contributed, directly or indirectly, to its success. ~\\
My special thanks go to: ~\\
         \vspace{2\baselineskip}


\textbf{Ms. Farah BARIKA KTATA}, teacher at ISSAT Sousse, ~\\
for her supervision, assistance, and rigor, which helped me a lot in the ~\\
drafting of this report. ~\\
         \vspace{2\baselineskip}

\textbf{Ms. Rim BEN ABDESSLEM} and \textbf{Mr. Mandour AROUS} Developers at TechLead,~\\
\textbf{Ms. Noura ELABED}, head of TechLead, ~\\
for their guidance, advice, and support. ~\\
Thank you for the invaluable experience and the positive impact you have had on my career. ~\\
         \vspace{2\baselineskip}


My sincere gratitude to all \textbf{ISSAT} faculty, for the training they gave us. ~\\
         \vspace{2\baselineskip}


I end these thanks by warmly greeting the members of the jury for ~\\

the honor they do me by agreeing to judge this work. ~\\
\end{center}


\cleardoublepage%
